%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage{multicol}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.87]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Scott}{Morgan}
%\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
%\address{51 Gregory Close, Pencoed, Bridgend, CF35 6RF}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{+44 7725 131355}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{MorganSN@cardiff.ac.uk}                               % optional, remove / comment the line if not wanted
\homepage{scott3142.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{A dedicated and committed individual with a strong passion for education, teaching and learning.}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

%packages added by me
\usepackage{eurosym}
\usepackage{amstext} % for \text
\DeclareRobustCommand{\officialeuro}{%
	\ifmmode\expandafter\text\fi
	{\fontencoding{U}\fontfamily{eurosym}\selectfont e}}

\begin{document}
	%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
	%-----       resume       ---------------------------------------------------------
	\makecvtitle
	\vspace{-10mm}
	\section{Education}
	
	\vspace{10pt}
	
	\subsection{Academic Qualifications}
	
	\vspace{5pt}
	
	\begin{itemize}
		
		\item{\cventry{2014 -- Present}{PhD Applied Mathematics: \textit{In Progess}}{Cardiff University}{}{}{}}
		\vspace{3pt}
		\item{\cventry{2010 -- 2014}{MMath Mathematics: First Class Honours, Best in School}{Cardiff University}{}{}{}}
		
	\end{itemize}
	
	\vspace{10pt}
	
	\subsection{Research Projects}
	
	\vspace{5pt}
	
	\begin{itemize}
		
		\item{\textbf{PhD Thesis:} \textit{Stability of Periodically Modulated Rotating Boundary Layers}		
			
			\vspace{3pt}
			
			\begin{itemize}
				\item [-] \small{\textbf{Supervisor:} \textit{Dr. Christopher Davies}}
				\item [-] \small{\textbf{Synopsis:} \textit{To investigate the stabilising effects of adding modulation to a rotating disk boundary layer.}}
			\end{itemize}														
		}
	
		\vspace{10pt}
		
		\item{\textbf{MMath Thesis:} \textit{Topics in Oscillatory Flow}		
			
			\vspace{3pt}
			
			\begin{itemize}
				\item [-] \small{\textbf{Supervisor:} \textit{Dr. Christopher Davies}}
				\item [-] \small{\textbf{Synopsis:} \textit{To investigate the connection between the local and global stability analyses of an oscillatory Stokes layer.}}
			\end{itemize}														
		}
		
		\vspace{10pt}
	
		\item{\textbf{Undergraduate Project (CUROP):} \textit{Boundary Layer Flows with an Oscillatory Rotation Rate}		
			
			\vspace{3pt}
			
			\begin{itemize}
				\item [-] \small{\textbf{Supervisor:} \textit{Dr. Christopher Davies}}
				\item [-] \small{\textbf{Synopsis:} \textit{To develop an efficient numerical algorithm for solving a system of nonlinear time-dependent differential equations.}}
			\end{itemize}														
		}
		
	\end{itemize}
	
	\vspace{10pt}
	
	\subsection{Academic Awards}
	
	\vspace{5pt}
	
	%\begin{multicols}{2}
		\begin{itemize}
			
			\item{\textbf{Recognition for Outstanding Contribution (2017)} - \small{\textit{Society of Industrial and Applied Mathematics}}}
			
			\vspace{6pt}
			
			\item{\textbf{Best in School Prize (2014)} - \small{\textit{Cardiff University}}}
			
			\vspace{6pt}
			
			\item{\textbf{Second Year Prize (2013)} - \small{\textit{Cardiff University}}}
			
			\vspace{6pt}
			
			\item{\textbf{First Year Prize (2012)} - \small{\textit{Cardiff University}}}
			
			\vspace{6pt}
			
			\item{\textbf{Calculus Prize (2011)} - \small{\textit{Cardiff University}}}
			
		\end{itemize}
	%\end{multicols}
	
	\vspace{10pt}
	
	\section{Teaching Experience}
	
	\vspace{10pt}
	
	\begin{itemize}
		
		\item{\cventry{January 2018 -- Present}{Associate Lecturer}{Cardiff University}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Delivered a second year undergraduate module \textit{Elementary Fluid Dynamics} for 70 students.
					\item Achieved 96\% overall positive final feedback from students.
				\end{itemize}
		}}
		
		\vspace{6pt}
		
		\item{\cventry{September 2016 -- Present}{Computing Consultant and Associate Lecturer}{Bridgend College}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Devised, composed and delivered units for BTEC Levels 2, 3 \& 4 in Automated Systems, Control Systems and Website Design \& Development.
					\vspace{3pt}
					\item Delivered CPD training sessions to staff at Bridgend College using Raspberry Pi, Python and BBC Micro:bit.
					\vspace{3pt}
					\item Worked closely with industrial partners and participated in regional and national  events such as the Urdd Eisteddfod, World Skills, STEM fairs and Senedd exhibitions to showcase projects to local schools, businesses and Government. 
				\end{itemize}
		}}	
		
		\vspace{6pt}		
			
		\item{\cventry{March 2018 -- Present}{STEM Engagement Officer}{Cardiff University}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Personally selected to design and deliver intensive courses in the physical sciences as part of the university's \textit{step-up} scheme. Project involved tutorials and residential summer schools for A-Level students from traditionally disadvantaged backgrounds.
					\vspace{3pt} 
					\item Responsible for First Campus primary school project on wearable technology using BBC Micro:bit. 
				\end{itemize}
		}}
	
		\vspace{6pt}
	
		\item{\cventry{October 2014 -- Present}{Postgraduate Demonstator}{Cardiff University}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Devised, composed and delivered an 11-week intensive course titled \textit{An Introduction to MATLAB} to final-year undergraduates and postgraduates.
					\vspace{3pt} 
					\item Led weekly classroom based tutorial sessions on a wide variety of topics including Calculus, Group Theory, Analysis, Differential Equations and Computing.
					\vspace{3pt}
					\item Instructor in weekly drop-in sessions, handling a wide range of mathematics-based queries from students in many fields including Engineering, Physics, Economics, Biology and Chemistry. 
				\end{itemize}
		}}
		
		\vspace{6pt}
		
		\item{\cventry{January 2018 -- Present}{Session Tutor}{Further Mathematics Support Programme}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Designed and delivered a series of sessions designed to teach students a range of subjects for Further Mathematics A-Level.
				\end{itemize}
		}}

		\vspace{6pt}
		
		\item{\cventry{January 2018 -- Present}{Scholars Programme Tutor}{The Brilliant Club}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Successful in application to Brilliant Club PhD Scholars programme.
					\vspace{3pt} 
					\item Developed and ran short courses aimed at talented KS3 and KS4 students from traditionally disadvantaged backgrounds.
					\vspace{3pt} 
					\item Received pedagogical training through intensive workshop sessions.
				\end{itemize}
		}}
		
		\vspace{6pt}
		
		\item{\cventry{February 2017 -- Present}{Raspberry Pi Certified Educator}{Picademy}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Successful in application to Brilliant Club PhD Scholars programme.
					\vspace{3pt} 
					\item Developed resources and delivered extensive CPD sessions to staff at Bridgend College based around control technologies, computing and programming.
				\end{itemize}
		}}

		\vspace{6pt}
		
		\item{\cventry{February 2017 -- Present}{STEM Ambassador}{STEM Learning}{}{}{\vspace{3pt}
				\begin{itemize}
					\item Organised and ran several workshops based around computing and control technologies at primary and secondary schools in Bridgend, Cardiff and Bristol.
				\end{itemize}
		}}
				
	\end{itemize}

	\vspace{10pt}
	
	\section{Other Notable Contributions}
	
	\vspace{10pt}
	
	\begin{itemize}
		
		\item{\textbf{Founding member of UKFN SIG on boundary layers and complex rotating flows} \hfill \textit{(2017 -- Present)}
			
			\vspace{4pt}
			
			\small{
				\begin{itemize}	
					\item Heavily involved in SIG activities including conference organisation and collaborations across universities.
					\vspace{3pt}
					\item Awarded competitive £600 grant for \textit{short research visits} to Leicester, Warwick and Coventry to develop collaborative ties. 
				\end{itemize}
				
		}}
		
		\vspace{6pt}
		
		\item{\textbf{Cardiff SIAM-IMA Student Chapter President} \hfill\textit{(2015 -- 2017)}
			
			\vspace{4pt}
			
			\small{
				\begin{itemize}	
					\item Secured competitive grant funding totalling over £2000 for conference travel and public engagement workshop sessions including external workshops on robotics, 3D printing and Raspberry Pi. Article published in \textit{Mathematics Today}.
					\vspace{3pt}
					\item Received \textit{Recognition for Outstanding Contribution} award for public engagement and chapter activities.
					\vspace{3pt}
					\item Organised and hosted the SIAM National Student Chapter Conference at Cardiff University.
					\vspace{3pt}
					\item Arranged highly successful, weekly \textit{popular science} talks delivered by and to postgraduate students.
					\vspace{3pt}
					\item Organised \textit{3-minute thesis} competition for postgraduate students.	
					\vspace{3pt}
					\item Oversaw creation of new \textit{SIAM-IMA} chapter after securing grant funding from the IMA.
					\vspace{3pt}
					\item Developed chapter from small group of students to a recognised part of the school with an extended committee and many members from both the student and staff populations.
				\end{itemize}
		}}
		
		\vspace{6pt}
		
		\item{\textbf{BSA Cardiff Committee Member}\hfill \textit{(2017 -- Present)}
			
			\vspace{4pt}
			
			\small{
				\begin{itemize}	
					\item Actively involved in organisation of activities including Cardiff \textit{Science Cafe} and events for British Science Week.
				\end{itemize}
		}}
		
	\end{itemize}
	
	\vspace{10pt}
	
	\section{Publications}
	
	\vspace{10pt}
	
	\begin{itemize}
		\item Scott Morgan, Christopher Davies, \textit{Linear stability analysis of steady and temporally periodic flow configurations using a velocity-vorticity formulation} (\textit{in draft})
		
		\vspace{6pt}
		
		\item Scott Morgan, Christopher Davies, \textit{Stability of rotating disk boundary layers with a periodically modulated rotation rate} (\textit{in draft})
	\end{itemize}
	
	\vspace{10pt}
	
	\section{Funding Awarded}
	%\begin{multicols}{2}
		
		\vspace{8pt}
		
		\begin{itemize}
		
			\item \textbf{Research:}
			
			\vspace{6pt}
			
			\begin{itemize}
				
				\item \textbf{EPSRC Postgraduate Research Studentship} \hfill \textit{(2014-2018)} \\
				\textit{£13,863 p/a (3.5 years)}
				
				\vspace{2pt}
				
				\item \textbf{SIAM Student Travel Award} \hfill\textit{(2018)}\\
				\textit{£70}
				
				\vspace{2pt}
				
				\item \textbf{UKFN Short Research Visit Grant} \hfill\textit{(2018)}\\
				\textit{£600}
				
				\vspace{2pt}
				
				\item \textbf{SIAM UKIE Travel Award} \hfill\textit{(2018)}\\
				\textit{£80}
				
				\vspace{2pt}
				
				\item \textbf{SIAM SNSCC Travel Award} \hfill \textit{(2017)}\\
				\textit{\euro{}150}
				
				\vspace{2pt}
				
				\item \textbf{SIAM Student Travel Award} \hfill\textit{(2017)}\\
				\textit{\$800}
				
				\vspace{2pt}
				
				\item \textbf{ERCOFTAC Travel Award} \hfill\textit{(2017)}\\
				\textit{\euro{}220}

				\vspace{2pt}
				
				\item \textbf{SIAM Student Representative Award} \hfill \textit{(2016)}\\
				\textit{\$700}
				
				\vspace{2pt}
				
				\item \textbf{Cardiff Undergraduate Research Opportunities Program (CUROP)} \hfill\textit{(2013)} \\
				\textit{£1600 (8 weeks)}
				
			\end{itemize}
			
			\vspace{6pt}
			
			\item \textbf{Outreach:}
				
			\vspace{6pt}
			
			\begin{itemize}
				
				\item \textbf{Royal Society of Chemistry Large Outreach Funding} \hfill\textit{(2018-2019)}\\
				\textit{£10000}
				
				\vspace{2pt}
				
				\item \textbf{First Campus Primary Aspirations} \hfill\textit{(2018)}\\
				\textit{£2500}
				
				\vspace{2pt}
				
				\item \textbf{LMS Education Grant} \hfill\textit{(2018)}\\
				\textit{£425}

				\vspace{2pt}
				
				\item \textbf{IMA Education Grant} \hfill\textit{(2017)}\\
				\textit{£400}
				
				\vspace{2pt}
				
				\item \textbf{Cardiff University Widening Access Funding} \hfill\textit{(2017)}\\
				\textit{£500}
				
			\end{itemize}
				
		
		\end{itemize}
	%\end{multicols}
	
	\vspace{10pt}
	
	\section{Major Conferences \& Workshops}
	
	\vspace{8pt}
	
	\begin{itemize}
		
		\item{\textbf{Hosted \& Organised:} 
			\small{
				\begin{itemize}
					\vspace{3pt}
					\item 5th SIAM National Student Chapter Conference \hfill \textit{Cardiff University (2016)}
		\end{itemize}}}
		
		\vspace{6pt}
		
		\item{\textbf{Invited Talk:}
			
			\small{
				\begin{itemize}
					\vspace{3pt}
					\item Engineering Department Seminar Series \hfill \textit{Warwick (2018)}
					\vspace{3pt}
					\item Department of Engineering Seminar Series \hfill \textit{Leicester (2017)}
					\vspace{3pt}
					\item Cardiff Science Cafe \hfill \textit{Cardiff (2017)}
		\end{itemize}}}
		
		\vspace{6pt}
		
		\item{\textbf{Contributed Talk:}
			%\begin{multicols}{2}
				\small{
					\begin{itemize}
						\vspace{3pt}
						\item Welsh Mathematics Colloquium \hfill \textit{Gregynog (2018)}
						\vspace{3pt}
						\item PyDiff \hfill \textit{Cardiff (2018)}
						\vspace{3pt}
						\item DiPaRT \hfill \textit{Bristol (2017)}
						\vspace{3pt}
						\item UKFN SIG: Boundary layers and complex rotating flows \hfill \textit{Warwick (2017)}
						\vspace{3pt}
						\item SIAM Annual Meeting \hfill \textit{Pittsburgh (2017)}
						\vspace{3pt}
						\item ERCOFTAC SIG33 Workshop \hfill \textit{Siena (2017)}
						\vspace{3pt}
						\item 6th SIAM National Student Chapter Conference \hfill \textit{Galway (2017)}
						\vspace{3pt}
						\item Welsh Mathematics Colloquium \hfill \textit{Gregynog (2017)}
						\vspace{3pt}
						\item Welsh Mathematics Colloquium \hfill \textit{Gregynog (2016)}
		\end{itemize}}
	%\end{multicols}
	}
		\vspace{6pt}
		\item{\textbf{Contributed Poster:}
			\small{
				\begin{itemize}
					\vspace{3pt}
					\item SIAM UKIE Annual Meeting \hfill \textit{University of Southampton (2018)}
					\vspace{3pt}
					\item SIAM UKIE 20th Annual Meeting \hfill \textit{University of Cambridge (2016)}
		\end{itemize}}}
		
	\end{itemize}

	%\section{References}
	
	%\vspace{6pt}
	
	%\begin{itemize}
	
	%\item{Available on request}
	
	%\end{itemize}
	
	%\newpage
	
	%\section{Technical Skills}
	
	%\vspace{6pt}
	
	%\begin{itemize}
	
	%\item \textbf{Programming \& Software:} 
	%\begin{itemize}
	%\vspace{3pt}
	%\item Proficient in: MATLAB, Fortran, Python, TeX, HTML, PHP, CSS, git, bash
	%\vspace{3pt}
	%\item Basic ability with: Mathematica, C++, JavaScript
	%\end{itemize}
	
	%\vspace{6pt}
	
	%\item \textbf{Other:} 
	%\begin{itemize}
	%\vspace{3pt}
	%\item Excellent oral and written communication skills from extensive report writing and discussion of my work with a large variety of people.
	%\vspace{3pt}
	%\item Strong interpersonal skills due to extensive teaching experience.
	%\vspace{3pt}
	%\item Highly developed organisational skills acquired from organising conferences and student events.
	%\end{itemize}
	
	%\vspace{6pt}
	
	%\end{itemize}
	
	% Publications from a BibTeX file without multibib
	%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
	%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
	%\nocite{*}
	%\bibliographystyle{plain}
	%\bibliography{publications}                        % 'publications' is the name of a BibTeX file
	
	% Publications from a BibTeX file using the multibib package
	%\section{Publications}
	%\nocitebook{book1,book2}
	%\bibliographystylebook{plain}
	%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
	%\nocitemisc{misc1,misc2,misc3}
	%\bibliographystylemisc{plain}
	%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file
	
	%-----       letter       ---------------------------------------------------------
	
\end{document}


%% end of file `template.tex'.
